---
title: "Plot Graph Types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot Graph Types}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nanoscopeAFM)
library(ggplot2)
library(scales)
```

## Loading AFM image

```{r}
fname = AFM.getSampleImages()[1]
afmd = AFM.import(fname)
```

The AFM image can be displayed using graphTypes:

## graphType 1

This is the basic and default graph for an AFM image:

```{r}
q = plot.AFMdata(afmd, graphType=1, trimPeaks=0.01)
```

## graphType 2

This graph has a square shape and adds a bar of length 20%; it places the scale inside the graph.

```{r}
plot.AFMdata(afmd, graphType=2,trimPeaks=0.01)
```

The image can be saved with `ggsave` as it is graphed with ggplot.

```{r}
g1 = plot.AFMdata(afmd, graphType=2, size=10, trimPeaks=0.01)
ggsave(tempfile(pattern = "", fileext = ".png"), plot=g1, dpi=150)
```

## graphType 3

This graph type is bare and has neither length scales nor legend.

```{r}
plot.AFMdata(afmd, graphType=3, trimPeaks=0.01)
summary(afmd)
```
## graphType 4

This graph type is plain with a scale. You can also change the color and the size of the font that displays the scale.

```{r}
plot.AFMdata(afmd, graphType=4, col='white', size=10, trimPeaks=0.05, fillOption = 'A')
```



## Red Blue Color Scheme

This graph type is bare and has neither length scales nor legend.

```{r}
plot.AFMdata(afmd, graphType=1, trimPeaks=0.01, redBlue = TRUE)
```



## Graphing 2 plots side by side

Use the package `cowplot` to create a graph with two plots. Use `save_plot` to save the graph.

```{r}
library(cowplot)
fname2 = AFM.getSampleImages(type='ibw')[1]
afmd2 = AFM.import(fname2)
summary(afmd2)
g1 = plot.AFMdata(afmd, trimPeaks=0.01, graphType = 1)
g2 = plot.AFMdata(afmd2, no=2, trimPeaks=0.01, graphType = 1, mpt=29.6)
g3 = plot.AFMdata(afmd, no=3, trimPeaks=0.01, graphType = 1, mpt=65.5)
g4 = plot.AFMdata(afmd, no=4, trimPeaks=0.01, graphType = 1)
gAll = plot_grid(g1, g2, g3, g4,
          labels=c('a','b','c','d'))
ggdraw(add_sub(gAll, "(a) height, (b) amplitude, (c) phase, (d) z sensor",x=0.1, hjust=0))
```


## Changing the Color Palette

You can use the `fillOption` option to change the color palette, see also `? scale_fill_viridis`. There are 8 options:


```{r}
plot.AFMdata(afmd, graphType = 1, fillOption = "magma")
plot.AFMdata(afmd, graphType = 1, fillOption = "inferno")
plot.AFMdata(afmd, graphType = 1, fillOption = "plasma")
plot.AFMdata(afmd, graphType = 1, fillOption = "viridis")
```

```{r}
plot.AFMdata(afmd, graphType = 1, fillOption = "cividis")
plot.AFMdata(afmd, graphType = 1, fillOption = "rocket")
plot.AFMdata(afmd, graphType = 1, fillOption = "mako")
plot.AFMdata(afmd, graphType = 1, fillOption = "turbo")
```


## Adjusting the scale

```{r}
plot.AFMdata(afmd)
plot.AFMdata(afmd, setRange=c(-50,50))
```
